\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-13 analytics.tex
Cheeseball

In this chapter I propose three hypotheses. They are:

@@

  \item Skedge’s \emph{navigations-per-add} demonstrate the \textbf{effectiveness of its search features} for each of the following three user search paradigms:

  \begin{enumerate}
    \item direct search,
    \item exploratory search, and
    \item peer-guided search
  \end{enumerate}

@@

\noindent In the following sections I will present my analysis on collected usage data since November 3rd 2015, which will serve to validate each hypothesis.

>>>>

In this chapter I propose three hypotheses, each to be supported by analysis in the coming sections. The hypotheses are:

@@

  \item Skedge’s \emph{navigations-per-add} demonstrate its \textbf{effectiveness} in the user search paradigms of \textbf{a) direct search} and \textbf{b) exploratory search}.

@@

### 2016-04-13 analytics/usage.tex
Cheeseball

From November 3, 2015 to April 11, 2016 (a period of 159 days), Skedge has seen\ldots

\begin{center}
\begin{tabular}{l}
  \hline
  4,713 users that have added or bookmarked at least one course \\ 
  5,256 schedules \\ 
  17,124 sessions\footnote{A session is defined by a period of activity expiring after 30 minutes of inactivity}, 75\% of which are from returning visitors \\ 
  107 sessions averaged per day \\ 
  5.4 pages viewed averaged per session  \\ 
  6 minutes spent averaged per session \\ 
  \hline
\end{tabular}
\end{center}

\vspace{10pt}

\noindent In this section, I will address many of the features listed in Chapter 2 (Design) and demonstrate their usability.

@@

I hypothesize that a combination of Skedge's presentation of information, its highly interactive user interface, and its concern for quality of user experience contribute to a sense of enjoyment regarding course scheduling. Clicking an average of five times \emph{per session} corresponds to clicking on the blocks for each of his or her courses, glancing over the details, and perhaps reading over the course description. This enamorment with one's course selection is a large component of Skedge's mission. It may seem trivial to state, but I believe the courses one takes in college are paramount to one's personal development and outlook on life. I believe ensuring that students are excited about their course selection and can also freely explore what more knowledge their university has to offer them is key to a well-balanced college experience.

The above could only be confirmed with involved user studies, which I do not have any data for. At the very least, the average block-clicks per session is a strong case for Skedge's usability over CDCS for the simple reason that Better CDCS does not even allow users to click on their schedule blocks, and this usage data shows that there is clearly a desire to do so.

>>>>

In this section, I will address many of the features listed in Chapter 2 (Design) and demonstrate their usability. As an overview, since November 3, 2015 (159 days ago), Skedge has seen\ldots

\begin{center}
\begin{tabular}{l}
  \hline
  4,713 users that have added or bookmarked at least one course \\ 
  5,256 schedules, with an average of 5.13 and median of 5 sections per schedule \\ 
  17,124 sessions, 75\% of which are from returning visitors \\ 
  107 sessions averaged per day \\ 
  5.4 pages viewed averaged per session  \\ 
  6 minutes spent averaged per session \\ 
  \hline
\end{tabular}
\end{center}

The figure of 4,713 total users may be a little misleading,

\begin{itemize}
  \item 
\end{itemize}

@@

I hypothesize that a combination of Skedge's presentation of information, highly interactive user interface, and concern for quality of user experience contributes to a sense of enjoyment in course scheduling. Five clicks corresponds to five courses (both the median and mean for sections per schedule is 5), meaning that in every session, a user could be reviewing details and reading over descriptions for each of their courses. Enabling this sense of pride and admiration with one's course selection is a crucial aspect of Skedge's mission. I believe the courses one chooses to take are an integral aspect of one's personal development and outlook on life in college. I believe ensuring that students are excited not only about their courses, but also about \emph{exploring} what their university has to offer is key to an inspired, intellectually curious student body.

The above could only be confirmed with involved user studies, for which I have no data. At the very least, the average block-clicks per session is a strong case for Skedge's usability over CDCS for the simple reason that Better CDCS does not even allow users to click on their schedule blocks, and this usage data shows that there is clearly a desire to do so.

### 2016-04-13 conclusion.tex
Cheeseball

While I am aware that such matters are not extremely pressing, they nevertheless degrade student experience on campus and discolor perception of the administration's care for students, especially when modern, relevant, and engaging tools are within arm's reach, and \emph{most} especially at a time when University of Rochester's very high tuition rates continue to rise year-to-year.

As a graduating senior, I cannot commit to continuing the upkeep of server costs and system maintenance for Skedge in the long term, and certainly not indefinitely. For the sake of the University's students, parents, faculty, and staff, I hope that my efforts with Skedge were not in vain and can lead to a substantial refresh of University tools that, most crucially, \textbf{involves a dialogue between the administration, students, and staff}. Thank you for reading.

>>>>

While functional, CDCS nevertheless degrades student experience on campus and discolors perception of the administration's care for students, especially when modern, relevant, and engaging tools are within arm's reach, and most especially at a time when University of Rochester's very high tuition rates continue to rise year-to-year.

As a graduating senior, I cannot commit to continuing the upkeep of server costs and system maintenance for Skedge in the long term, and certainly not indefinitely. For the sake of the University's students, parents, faculty, and staff, I hope that my efforts with Skedge were not in vain and can lead to a substantial refresh of University tools that, most crucially, \textbf{involves a dialogue between the administration, students, and staff}. Thank you.
